---
title: " MRI Knee Path- Using Deep Learning Models - Spring 2026 "
subtitle: "This is a Report Template Quarto"
author: "Bala Raju Pidatala & Sabna Balasubramoniapillai (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

Slides: [slides.html](slides.html){target="_blank"} ( Go to `slides.qmd`
to edit)

::: callout-important
**Remember:** Instead of removing everything keeping the details 
and removing the unnecessary content!
:::

## Introduction


*This is an introduction to ..... regression, which is a non-parametric
estimator that estimates the conditional expectation of two variables
which is random. The goal of a kernel regression is to discover the
non-linear relationship between two random variables. To discover the
non-linear relationship, kernel estimator or kernel smoothing is the
main method to estimate the curve for non-parametric statistics. In
kernel estimator, weight function is known as kernel function
[@efr2008]. Cite this paper [@bro2014principal]. The GEE [@wang2014].
The PCA [@daffertshofer2004pca]*. Topology can be used in machine
learning [@adams2021topology]

For Symbolic Regression [@wang2019symbolic] *This is my work and I want
to add more work...*

Cite new paper [@su2012linear]

Classification of Knee OA was studied here [@guida2021knee]

## Methods


*Another equation:*

$$
F(x) = H(x)-x
$$

## Analysis and Results

### Data Exploration and Visualization

```{r, warning=FALSE, echo=T, message=FALSE}
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
```

```{python}
import pandas as pd
```

```{r, warning=FALSE, echo=TRUE}
# Load Data
kable(head(murders))

ggplot1 = murders %>% ggplot(mapping = aes(x=population/10^6, y=total)) 

  ggplot1 + geom_point(aes(col=region), size = 4) +
  geom_text_repel(aes(label=abb)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(formula = "y~x", method=lm,se = F)+
  xlab("Populations in millions (log10 scale)") + 
  ylab("Total number of murders (log10 scale)") +
  ggtitle("US Gun Murders in 2010") +
  scale_color_discrete(name = "Region")+
      theme_bw()
  

```

### Modeling and Results

-   Explain your data preprocessing and cleaning steps.


-   **Tell a story about what the data reveals.**

```{r}

```

### Conclusion


## References
