---
title: " MRI Knee Path- Using Deep Learning Models - Spring 2026 "
subtitle: "This is a Report Template Quarto"
author: "Bala Raju Pidatala & Sabna Balasubramoniapillai (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

Slides: [slides.html](slides.html){target="_blank"} ( Go to `slides.qmd`
to edit)

::: callout-important
**Remember:** Instead of removing everything keeping the details 
and removing the unnecessary content!
:::

## Introduction


*This is an introduction to ..... regression, which is a non-parametric
estimator that estimates the conditional expectation of two variables
which is random. The goal of a kernel regression is to discover the
non-linear relationship between two random variables. To discover the
non-linear relationship, kernel estimator or kernel smoothing is the
main method to estimate the curve for non-parametric statistics. In
kernel estimator, weight function is known as kernel function
[@efr2008]. Cite this paper [@bro2014principal]. The GEE [@wang2014].
The PCA [@daffertshofer2004pca]*. Topology can be used in machine
learning [@adams2021topology]

For Symbolic Regression [@wang2019symbolic] *This is my work and I want
to add more work...*

Cite new paper [@su2012linear]

Classification of Knee OA was studied here [@guida2021knee]

Related Papers & Their Summaries:

1. Early diagnosis of the severity of knee osteoarthritis using vision transformer: This model utilizes Vision Transformers (ViT) instead of CNNs, which can help the AI model learn the overall features of the knee joint, thereby improving the detection of early-stage knee osteoarthritis, as CNNs are limited to recognizing individual pixels.
[@panwar2025early]

2. Federated knee injury diagnosis using few shot learning: This model utilizes the federated learning approach with few shot learning, which can help the AI model learn from multiple hospitals without compromising the data privacy of the patients, thereby improving the detection of knee injuries despite the limited data available.
[@goel2025federated]

3. Self-Supervised Learning with BYOL for ACL Tear Detection: It utilizes self-supervised learning with the Bootstrap Your Own Latent (BYOL) algorithm for the detection of ACL tears. It uses the BYOL self-supervised learning algorithm to pre-train the ResNet-18 model for feature extraction of the knee MRI scans.
[@aidarkhan2025self]

4. Moving Beyond Traditional Orthopaedic Data Analysis: It shows the effectiveness of using multimodal AI models that utilize MRI image data along with electronic health record data for the diagnosis of orthopaedic problems.
[@oettl2025beyond]

## Methods


*Another equation:*

$$
F(x) = H(x)-x
$$

## Analysis and Results

### Data Exploration and Visualization

```{r, warning=FALSE, echo=T, message=FALSE}
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
```

```{python}
import pandas as pd
```

```{r, warning=FALSE, echo=TRUE}
# Load Data
kable(head(murders))

ggplot1 = murders %>% ggplot(mapping = aes(x=population/10^6, y=total)) 

  ggplot1 + geom_point(aes(col=region), size = 4) +
  geom_text_repel(aes(label=abb)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(formula = "y~x", method=lm,se = F)+
  xlab("Populations in millions (log10 scale)") + 
  ylab("Total number of murders (log10 scale)") +
  ggtitle("US Gun Murders in 2010") +
  scale_color_discrete(name = "Region")+
      theme_bw()
  

```

### Modeling and Results

-   Explain your data preprocessing and cleaning steps.


-   **Tell a story about what the data reveals.**

```{r}

```

### Conclusion


## References
