---
title: " MRI Knee Path- Using Deep Learning Models - Spring 2026 "
subtitle: "This is a Report Template Quarto"
author: "Bala Raju Pidatala & Sabna Balasubramoniapillai (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

Slides: [slides.html](slides.html){target="_blank"} ( Go to `slides.qmd`
to edit)

::: callout-important
**Remember:** Instead of removing everything keeping the details 
and removing the unnecessary content!
:::

## Introduction
This research reviews the application of deep learning (DL) models for diagnosing knee pathologies using MRI scans.
Focuses on the performance and clinical relevance of convolutional neural networks (CNNs) in assisting medical professionals.
Summarizes current approaches, strengths, and limitations in recent scientific literature.
Highlights advances in automated diagnosis, dataset usage, and the role of validation/regulatory standards.
Examines the extent to which current deep learning approaches match or exceed expert diagnostic accuracy.


Related Papers & Their Summaries:

1. Early diagnosis of the severity of knee osteoarthritis using vision transformer: This model utilizes Vision Transformers (ViT) instead of CNNs, which can help the AI model learn the overall features of the knee joint, thereby improving the detection of early-stage knee osteoarthritis, as CNNs are limited to recognizing individual pixels.
[@panwar2025early]

2. Federated knee injury diagnosis using few shot learning: This model utilizes the federated learning approach with few shot learning, which can help the AI model learn from multiple hospitals without compromising the data privacy of the patients, thereby improving the detection of knee injuries despite the limited data available.
[@goel2025federated]

3. Self-Supervised Learning with BYOL for ACL Tear Detection: It utilizes self-supervised learning with the Bootstrap Your Own Latent (BYOL) algorithm for the detection of ACL tears. It uses the BYOL self-supervised learning algorithm to pre-train the ResNet-18 model for feature extraction of the knee MRI scans.
[@aidarkhan2025self]

4. Moving Beyond Traditional Orthopaedic Data Analysis: It shows the effectiveness of using multimodal AI models that utilize MRI image data along with electronic health record data for the diagnosis of orthopaedic problems.
[@oettl2025beyond]

5. Classification of Knee OA was studied here [@guida2021knee]


## Methods


*Another equation:*

$$
F(x) = H(x)-x
$$

## Analysis and Results

### Data Exploration and Visualization

```{r, warning=FALSE, echo=T, message=FALSE}
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
```

```{python}
import pandas as pd
```

```{r, warning=FALSE, echo=TRUE}
# Load Data


```

### Modeling and Results

-   Explain your data preprocessing and cleaning steps.


-   **Tell a story about what the data reveals.**

```{r}

```

### Conclusion


## References
